Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
More edits.

Another selection construct in Haskell is pattern matching. Pattern matching is a simple way to have a 
function perform differently based on its input. It is initiatiated by defining a function multiple times in 
a row using patterns as parameters. The final declaration of the function must use a variable for the parameter 
in case the input does not match a pattern. The function will check the input against the patterns in order from 
first declared to last; thus, if the input does not conform to the first pattern, it will move on to the next pattern, and so on.

>>>>

Another selection construct in Haskell is pattern matching. Pattern matching is simply a way to have a 
function perform different actions based on its input. Pattern matching is done by defining a function multiple times in 
succession using patterns in place of parameters.  When the function is called, its arguments are checked against all patterns,
starting with the first and proceeding accordingly.  If no match is made, an exception is raised.
A default match can be speficied by listing `plain' variables as function parameters.
